---
title: "xcoredata"
author: "Maciej Migdał"
date: "`r Sys.Date()`"
output: html_vignette
vignette: >
  %\VignetteIndexEntry{xcoredata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

# Exploring the data in xcoredata

```{r}
library("xcoredata")
```

`xcoredata` contains the following objects, which can be accessed directly with
named functions:

```{r}
# FANTOM5 promoters
promoters_f5()
promoters_f5_core()

# ReMap2020 molecular signatures
remap_promoters_f5()
remap_meta()

# ChIP-Atlas molecular signatures
chip_atlas_promoters_f5()
chip_atlas_meta()
```

Alternatively, these objects can be accessed using the *ExperimentHub* interface,
eg.:

```{r}
library("ExperimentHub")

eh <- ExperimentHub()
query(eh, "remap_meta")
eh[["EH7299"]]
```

For details on these resources see object's documentation eg. `?remap_meta`.
The construction scripts are located under `inst/scripts`, especially look
into `inst/scripts/make-data.Rmd`.

